What do incoming university students believe about open science practices in

### 2021-10-17 analysis/Manuscript.Rmd
JB edits to intro and materials

# import the metadata [if using]
#metadata <- here::here("survey", "data", "students_metadata.csv") %>% 
 #read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
 #filter(!is.na(old_variable)) %>% 
 #dplyr::select (-c("...10", "note:"))

@@

Second, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice. This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done. On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility. For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values. The extent to which incoming psychology students may – or may not – be “naive open scientists” is useful knowledge for guiding pedagogical approaches.

We conducted a descriptive study examining the beliefs of incoming undergraduate students in a first-year psychology unit about reproducibility and open science practices in psychology. Our survey encompassed questions about norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is). Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses. We nevertheless preregistered our aims, sampling plan, exclusion criteria and data analysis plan at https://osf.io/6e2ux/?view_only=b5173ba3bf564bc495686cd0845e678b

<!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology?
-->

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

<!--MW: We need to include a link for accessing raw data and measures etc. -->

@@

Collaborators from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. An invitation was sent to participants via email or a course website 1-2 weeks before their course began. The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month, and included a link to the survey.

@@

<!--MW: I've moved Procedure up above Participants - I think that works better for flow since otherwise we have to describe screening within the survey before we've introduced the survey itself. Hope this is ok.-->

@@

The remaining `r n` participants were eligible based on starting their first unit 
of study in psychology at a university within the next month. For those individuals 
who were screened out, Qualtrics automatically directed them to a 
debriefing

Most participants reported that they were
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
their gender identity as "queer man", and `r gender[3,2]` participant reported 
non-binary gender.

@@

Most participants reported attending university in Australia (*n* = `r uni_country[1,2]`), 
the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). Nearly all reported graduating from high
school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
attended high school, fewer than half completed psychology courses in 
high school (*n* = `r hs_psyc[2,2]`). Most reported their nationality as being from Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = `r nationality[24,2]`), or China
(*n* = `r nationality[6,2]`). About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`).

<!--
MP: Seems like we are missing some nationalities here – US nationalities? NZ? Or is this just the top 3?
-->

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? -->
The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

There were 20 scenarios in total (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

<!-- Add Table X of norms and counternorms statements that map to each practice 
MW: The table captions/crossreferences may not be working - see the compiled document.

EK: for cross-referencing to work you can't have underscores in the chunk name
-->

@@

# recode the data so the response options have proper labels

# c <- metadata %>% 
#     filter(Scale == "OSmost") %>% 
#     filter(NewVariable != "OSmost_text") #remove this value from metadata
# 
# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>% 
#   rename ("OSmost_label" = "ItemText")

@@

We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm-counternorm pairs described above, albeit with one norm excluded on the basis of not referring to externally observable behaviour (critically evaluating published studies vs. accepting them), and one practice added out of interest (data sharing on request).  (see Table \@ref(tab:normsinpracticeitems)). Participants were given a slider bar ranging from 0% to 100% to record their estimate.

<!-- Add Table XX of 10 belief statements -->

```{r normsinpracticeitems}
practice_items = data.frame(
  "Practice" = c("Preregistration", "Registered reports", "p-hacking", "HARKing", "Info for replicability",
                 "Preprint", "open materials", "Open data", "Data on request", "Open access"),
  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
)

@@

#Note to selves: The norm in practice items map fairly closely to norms and counternorms, but not exactly
#I.e., there is no norm in practice item about critically evaluating published literature, but there is one about sharing
#data on request (which isn't in the norms/counternorms)
#I can't remember why we did this, but so it goes.
#The ordering of this table also doesn't match the one above, which I'm leaving for the moment since we probably want to set
#an order of items/norms and stick to it consistently throughout

>>>>

# import the metadata [if using]
# metadata <- here::here("survey", "data", "students_metadata.csv") %>%
# read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>%
# filter(!is.na(old_variable))

@@

Second, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice. This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done. On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility. For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted, with regard to their own analyses, “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values. The extent to which incoming psychology students may – or may not – be “naive open scientists” is useful knowledge for guiding pedagogical approaches.

We conducted a descriptive study examining the beliefs of incoming undergraduate students in a first-year psychology unit about reproducibility and open science practices in psychology. Our survey encompassed questions about norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is). Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses. We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp.

<!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology? JB: That'd be great in the 
abstract and discussion?
-->

# Methods
We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) --> Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6.

<!-- JB: Is there are a reason we aren't including Simmons et al as a cite? -->

@@

Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. An invitation was sent to participants via email or a course website 1–2 weeks before their course began. The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month, and included a link to the survey.

@@

<!-- JB: I've renamed collaborators to contacts because they aren't on this paper and aren't necessarily people that we've previously collaborated with. -->

<!--MW: I've moved Procedure up above Participants - I think that works better for flow since otherwise we have to describe screening within the survey before we've introduced the survey itself. Hope this is ok. JB: Fine with me. If it's an issue, we can describe the final sample of participants first and then describe the inclusion criteria later.-->

@@

The remaining `r n` participants were eligible based on starting their first unit 
of study in psychology at a university within the next month. Of the eligible 
participants, most reported that they were 18–24 years old (*n* = `r age[1,2]`);
`r age [2,2]` reported that they were 25–34 years old, `r age [3,2]` were 35–44 
years old, `r age [4,2]` were 45–54 years old, and `r age [5,2]` was 55–64 years old. 
The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
their gender identity as "queer man", and `r gender[3,2]` participant reported 
non-binary gender.

@@

Most participants reported attending university in Australia (*n* = `r uni_country[1,2]`), 
the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = 
`r uni_country[4,2]`). Nearly all reported graduating from high school or secondary 
school (*n* = `r hs_status[3,2]`). Of those participants who attended high school, 
fewer than half completed psychology courses in high school (*n* = `r hs_psyc[2,2]`).
Participants reported `r nrow(nationality)` different nationalities; the most 
common were Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = 
`r nationality[24,2]`), and China (*n* = `r nationality[6,2]`). About two-thirds of 
participants reported that at least one of their parents attended university 
(*n* = `r first_gen[2,2]`).

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

We presented 20 scenarios (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

@@

# c <- metadata %>%
#     filter(scale == "norms")

# add a practice column in metadata

# update this text  
# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>%
#   rename ("OSmost_label" = "ItemText")

@@

We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm–counternorm pairs described above, with two exceptions (see Table \@ref(tab:normsinpracticeitems)). We excluded one norm because it did not refer to externally observable behaviour (critically evaluating published studies vs. accepting them), and we included one practice out of interest (data sharing on request). Participants indicated their estimate on a slider bar ranging from 0% to 100%.

```{r normsinpracticeitems}
practice_items = data.frame(
  "Practice" = c("Preregistration", "Registered reports", "p-hacking", "HARKing", "Info for replicability",
                 "Preprint", "Open materials", "Open data", "Data on request", "Open access"),
  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
)

@@

#The ordering of this table also doesn't match the one above, which I'm leaving for the moment since we probably want to set
#an order of items/norms and stick to it consistently throughout
